### 2015-11-05 CVPR16/Source/abstract.tex
Added more comments about the experiments.

\begin{abstract}
This paper studies the problem of segmenting tracked feature points of multiple objects in a video sequence. We consider scenes that contain both dynamic and static objects, which usually appear in the context of autonomous driving (e.g., moving and parked cars), and occlusions among objects. We propose a novel continuous model for representing objects so that point tracks can be probabilistically and accurately assigned to the corresponding object while accounting for object occlusions. Detailed experiments on the KITTI dataset show the superiority of the propose method over the baseline method which simply uses detection bounding boxes for resolving occlusions and other state-of-the-art motion segmentation methods which cannot cope well with static objects. As a notable application, we show how our continuous occlusion model benefits the task of 3D localization in autonomous driving.  
\end{abstract}

>>>>

\begin{abstract}
This paper studies the problem of segmenting tracked feature points on multiple objects in a video sequence. We consider scenes that contain both dynamic and static objects, which usually appear in the context of autonomous driving (e.g., moving and parked cars), and occlusions among objects. We propose a novel continuous model for modeling objects so that point tracks can be probabilistically and accurately assigned to the corresponding object while accounting for object occlusions. Detailed experiments on the KITTI dataset show the superiority of the proposed method over the baseline method which simply uses detection bounding boxes for resolving occlusions and the state-of-the-art motion segmentation methods which cannot cope well with static objects. As a notable application, we show how our continuous occlusion model benefits the task of 3D localization in autonomous driving.  
\end{abstract}

### 2015-11-05 CVPR16/Source/applications.tex
Added more comments about the experiments.

\subsection{3D Object Localization}
To show the effectiveness of our method we apply it to the localization
problem. We estimate the position, orientation and dimensions of the car with
our framework and compute the error in birds eye view domain along the ground
plane. 
To estimate the localization of traffic participants (TPs) in a road scene we follow the graphical model approach.
We build the graphical model as shown in Fig~\ref{fig:graphmodel} that 
allows us to factorize the intractable probability distribution into following form
%
\begin{multline}
  -\log{P(\{\state{i}{t}\} | \mathbb{E})} = 
  -Z' 
  \\
  + \sum_{t=s_i}^{e_i}
  \left(
  \sum_{i,j:i\ne j}   
  \WEnergyCol 
   + \WpEnergy{bbox}
   + \WpEnergy{track}
\right)
  \\
  + \left(
  \sum_{i=1}^N 
  \WEnergy{lane}
  + \WEnergy{dyn}
  + \WEnergy{size}
\right)
  \enspace.
\end{multline}
%
Next, we explain the important energies used in our graphical model.

@@

\subsection{Metropolis Hastings Inference}
We use Metropolis Hastings' methods for graphical model inference. Since we are
optimizing over continuous random variables, we use Gaussian distribution as
the proposal distribution. We choose Metropolis Hastings inference over
block-coordinate descent which turns out to be slower than Metropolis Hastings
in our experiments. Please refer to our supplementary material for the comparison
of inference methods.

>>>>

\subsection{3D Object Localization}
To show the effectiveness of our method we apply it to the localization
problem. We estimate the position, orientation and dimensions of the car with
our framework and compute the error in birds eye view domain along the ground
plane. 
To estimate the localization of traffic participants (TPs) in a road scene we use the graphical model approach.
We build the graphical model as shown in Fig~\ref{fig:graphmodel} that 
allows us to factorize the intractable probability distribution into following form
%
\begin{multline}
  -\log{P(\{\state{i}{t}\} | \mathbb{E})} = 
  -Z' 
  \\
  + \sum_{t=s_i}^{e_i}
  \left(
  \sum_{i,j:i\ne j}   
  \WEnergyCol 
   + \WpEnergy{bbox}
   + \WpEnergy{track}
\right)
  \\
  + \left(
  \sum_{i=1}^N 
  \WEnergy{lane}
  + \WEnergy{dyn}
  + \WEnergy{size}
\right)
  \enspace.
\end{multline}
%
Next, we explain the important energies used in our graphical model.

@@

\subsection{Metropolis Hastings Inference}
We use Metropolis Hastings' methods \cite{mackay1998introduction} for graphical model inference. Since we are
optimizing over continuous random variables, we use Gaussian distribution as
the proposal distribution. We choose Metropolis Hastings inference over
block-coordinate descent which turns out to be slower than Metropolis Hastings
in our experiments. Please refer to the supplementary material for the
comparison of inference methods.

### 2015-11-05 CVPR16/Source/related.tex
Added more comments about the experiments.

\paragraph{Motion segmentation}
Motion segmentation has actively been studied in the literature. Previous work can roughly be categorized into algebraic methods~\cite{}, statistical methods~\cite{} and clustering methods~\cite{}. Some recent efforts include robust algebraic segmentation with hybrid perspective constraints~\cite{} and spectral clustering with point track spatial affinity~\cite{}. The above methods usually exploit the fact that point tracks of a particular moving object tend to follow similar motion patterns. Therefore, they cannot segment static objects due to no motion cues. In contrast, our method is relatively independent of object motions and hence does not suffer from static objects.

>>>>

\paragraph{Motion segmentation}
Motion segmentation has actively been studied in the literature. Previous work can roughly be categorized into algebraic methods~\cite{}, statistical methods~\cite{} and clustering methods~\cite{}. Some recent efforts include robust algebraic segmentation with hybrid perspective constraints~\cite{Rao_etal_2010} and spectral clustering with point track spatial affinity~\cite{Brox_Malik_2010}. The above methods usually exploit the fact that point tracks of a particular moving object tend to follow similar motion patterns. Therefore, they cannot segment static objects due to no motion cues. In contrast, our method is relatively independent of object motions and hence does not suffer from static objects.
